\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-08-13 doc/paper.tex
misc revisions

	\subsection{Implementation Details} The visualization is the product of two processes: \begin{itemize} \item \textit{Collection}: Given a set of
		Excel sheets, the tool, written in Java, uses Apache
		POI\footnote{https://poi.apache.org/} to identify and iterate over every cell
		containing a valid formula. Afterward, it calls POI's formula parser to break
		the formula text into an ordered set of individual tokens, which the tool then
		parses into the tree-like form. When all formulae have been analyzed like this,
		it produces JSON files for each top-level function in the set.

@@

	\subsection{Design Decisions} \label{ssec:decisions} Early in the design, we
	chose the tree form for its inherent ability to represent the parent-children
	relationship of formulae as functions and their arguments, which could be yet
	more functions. By adapting this structure for a broad range of possibilities
	for nested functions, the branching factor depends alternatively on the number
	of arguments in a function and the number of possible functions observed as an
	argument in a function.

	Another of our options was to represent the call trees as simple text
	hierarchies. Though this might work well for a single, uncomplicated call
	structure, we did not do this because our tool combined many of these call
	trees into a more complicated structure. To capture the different relationships
	in the tree and to quantify the frequency of arguments, we would need to be
	more verbose in our description. As such, we decided that visualizing some
	dimensions was quicker than writing them out.

	Guided by the goals in Section \ref{goals}, we faced a number of decisions in
	how to visualize the data. Below, we've outlined those that had the largest
	impact in the values that appear in the tree. \begin{itemize}

@@

		\item \textit{Importance of depth}: When a function appears within another,
		should it be analyzed only as a nested function or would it also be valid to
		analyze the nested function on its own?

		\ \ For example, in the pictured IF function, we found that people often use
		another IF statement as the second or third arguments of the top-level IF. If
		we only consider functions exactly where they're found embedded in the
		formula, then information about the same function -- IF, in this case -- will
		be scattered across different trees with no way to aggregate them. If we
		record every instance of a function by ignoring their context -- that is,
		including an IF embedded within a SUM function in the same node as the
		top-level IF -- then the tool will represent some functions in multiple nodes
		to capture every possible level of nesting. For now, we only include the
		first, with the latter to be added as an option in the future.

>>>>

	\subsection{Implementation Details} The visualization is the product of two processes: \begin{itemize} \item \textit{Collection}: Given a set of
		Excel sheets, the tool, written in Java, uses Apache
		POI\footnote{https://poi.apache.org/} to identify and iterate over every cell
		containing a valid formula. Afterward, it calls POI's formula parser to decompose
		the formula text into an ordered set of individual tokens, which the tool then
		parses into the tree-like form. When all formulae have been analyzed like this,
		it produces JSON files for each top-level function in the set.

@@

	\subsection{Design Decisions} \label{ssec:decisions} Early in the design, we
	chose the tree form for its inherent ability to represent the parent-children
	relationship of formulae as functions and their arguments, which could be yet
	more functions. One option that we did not take was to represent the call trees
	as simple text hierarchies. Though that might work well for a single,
	uncomplicated call structure, we did not do this because our tool combined many
	of these call trees into a more complicated structure. To capture the different
	relationships in the tree and to quantify the frequency of arguments, we would
	need to be more verbose in our description. As such, we decided that
	visualizing some dimensions was quicker than writing them out.

	In balancing this chosen form with the goals in Section~\ref{goals}, we faced a
	number of decisions in how to visualize the data. Below, we've outlined those
	that had the largest impact in the values that appear in the tree.
	\begin{itemize}

@@

		\item \textit{Importance of depth}: When a function appears within another,
		should it be analyzed only as a nested function or should \toolname
		analyze the nested function as a top-level function as well?

		\ \ For example, in the pictured \texttt{IF} function, we found that people often use
		another IF statement as the second or third arguments of the top-level \texttt{IF}. If
		we only consider functions exactly where they're found embedded in the
		formula, then information about the same function -- \texttt{IF}, in this case -- will
		be scattered across different trees with no way to aggregate them. If we
		record every instance of a function by ignoring their context -- that is,
		including an \texttt{IF} embedded within a \texttt{SUM} function in the same node as the
		top-level \texttt{IF} -- then the tool will represent some functions in multiple nodes
		to capture every possible level of nesting. For now, we only include the
		first, with the latter to be added as an option in the future.
